Multi-scale trend analysis of water quality using error propagation of generalized additive models

### 2020-11-15 manu_draft.Rmd
data objects, figures, tables changed from back-transformation fixes on wqtrends

p2a <- ggplot(toplo2, aes(x = SY, y = SYD)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  thm + 
  labs(
    title = '(b) Estimated chlorophyll (log-space) between models'
  )
p2b <- ggplot(toplo2, aes(x = SYD, y = SYDI)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  thm
p2c <- ggplot(toplo2, aes(x = SY, y = SYDI)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  thm

@@

p3a <- ggplot(toplo3, aes(x = SY, y = SYD)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  thm +
  labs(
    title = '(c) Estimated s(cont_year) between models'
    )
p3b <- ggplot(toplo3, aes(x = SYD, y = SYDI)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  thm
p3c <- ggplot(toplo3, aes(x = SY, y = SYDI)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  thm

@@

      prd <- anlz_prd(mod) %>% 
        anlz_backtrans()

@@

ylim <- c(0, 16)
ylab <- expression(paste("Chlorophyll-a (", mu, "g ", L^-1, ")"))

@@

pthm <- theme_bw(base_family = 'serif', base_size = 14) +
  theme(
    legend.position = 'top',
    strip.background = element_blank(),
    axis.title = element_blank(), 
    axis.text = element_text(size = 7)
  )

@@

p1 <- ggmap(bsmap1_transparent) +
  geom_point(data = toplo1, aes(x = lon, y = lat, size = abs(perchg), shape = persgn, fill = perchg, colour = pval)) + #, color = 'black') +
  geom_text(data = toplo1, aes(x = lon, y = lat, label = pval), nudge_x = 0.04) + 
  facet_grid( ~ yrs) + 
  scale_fill_gradient2('Chl-a % change', low = 'green', mid = 'white',  high = 'tomato1', midpoint = 0) +
  scale_colour_manual(values = c('black', 'black'), guide = F) +
  coord_map() + 
  scale_shape_manual('Trend', values = c(24, 25)) + 
  pthm +
  scale_size(range = c(1, 6), guide = F) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 6)) +
  labs(
    subtitle = '(a) Percent change between year pairs'
  )

p2 <- ggmap(bsmap1_transparent) +
  geom_point(data = toplo2, aes(x = lon, y = lat, size = abs(yrcoef), shape = coefsgn, fill = yrcoef, colour = pval)) + #, color = 'black') +
  geom_text(data = toplo2, aes(x = lon, y = lat, label = pval), nudge_x = 0.04) + 
  facet_grid(seas ~ yrs) + 
  scale_fill_gradient2(leglab2, low = 'green', mid = 'white',  high = 'tomato1', midpoint = 0) +
  scale_colour_manual(values = c('black', 'black'), guide = F) +
  coord_map() + 
  scale_shape_manual('Trend', values = c(24, 25)) + 
  pthm +
  scale_size(range = c(1, 6), guide = F) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 6)) +
  labs(
    subtitle = '(b) Annual rates of change across seasons by decade'
  )

>>>>

p2a <- ggplot(toplo2, aes(x = SY, y = SYD)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  scale_y_log10() + 
  scale_x_log10() + 
  thm + 
  labs(
    title = '(b) Estimated chlorophyll between models'
  )
p2b <- ggplot(toplo2, aes(x = SYD, y = SYDI)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  scale_y_log10() + 
  scale_x_log10() + 
  thm
p2c <- ggplot(toplo2, aes(x = SY, y = SYDI)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  scale_y_log10() + 
  scale_x_log10() + 
  thm

@@

p3a <- ggplot(toplo3, aes(x = SY, y = SYD)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  scale_y_log10() + 
  scale_x_log10() + 
  thm +
  labs(
    title = '(c) Estimated s(cont_year) between models'
    )
p3b <- ggplot(toplo3, aes(x = SYD, y = SYDI)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  scale_y_log10() + 
  scale_x_log10() + 
  thm
p3c <- ggplot(toplo3, aes(x = SY, y = SYDI)) + 
  geom_point(alpha = alph) + 
  geom_abline(slope = 1, intercept = 0, color = lncol) + 
  scale_y_log10() + 
  scale_x_log10() + 
  thm

@@

      prd <- anlz_prd(mod)

@@

ylim <- c(0, 21)
ylab <- expression(paste("Chlorophyll-a (", mu, "g ", L^-1, ")"))

@@

pthm <- theme_bw(base_family = 'serif', base_size = 12) +
  theme(
    legend.position = 'top',
    strip.background = element_blank(),
    axis.title = element_blank(), 
    axis.text = element_text(size = 8)
  )

@@

p1 <- ggmap(bsmap1_transparent) +
  geom_point(data = toplo1, aes(x = lon, y = lat, size = abs(perchg), shape = persgn, fill = perchg, colour = pval)) + #, color = 'black') +
  geom_text(data = toplo1, aes(x = lon, y = lat, label = pval), nudge_x = 0.04) + 
  facet_grid( ~ yrs) + 
  scale_fill_gradient2('Chl-a % change', low = 'green', mid = 'white',  high = 'tomato1', midpoint = 0) +
  scale_colour_manual(values = c('black', 'black'), guide = F) +
  coord_map() + 
  scale_shape_manual('Trend', values = c(24, 25)) + 
  pthm +
  scale_size(range = c(1, 6), guide = F) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 8)) +
  labs(
    subtitle = '(a) Percent change between year pairs'
  )

p2 <- ggmap(bsmap1_transparent) +
  geom_point(data = toplo2, aes(x = lon, y = lat, size = abs(yrcoef), shape = coefsgn, fill = yrcoef, colour = pval)) + #, color = 'black') +
  geom_text(data = toplo2, aes(x = lon, y = lat, label = pval), nudge_x = 0.04) + 
  facet_grid(seas ~ yrs) + 
  scale_fill_gradient2(leglab2, low = 'green', mid = 'white',  high = 'tomato1', midpoint = 0) +
  scale_colour_manual(values = c('black', 'black'), guide = F) +
  coord_map() + 
  scale_shape_manual('Trend', values = c(24, 25)) + 
  pthm +
  scale_size(range = c(1, 6), guide = F) +
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 8)) +
  labs(
    subtitle = '(b) Annual rates of change across seasons by decade'
  )
